Patient-Specific Neural Field Modeling from Mirco-Electrode Data

### 2010-07-19 ltx/data_paper/DataPaper.tex
minor correction to the estimation algorithm

where $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}[ \ln c-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to $\boldsymbol \theta$ and will disapear by differentiation, and

>>>>

where $\beta= \sum_{t=1}^T\mathbf E_{(\theta',\xi')}[ \ln \alpha-\mathbf x_{t+1}^\top\boldsymbol\Sigma_w^{-1}\mathbf x_{t+1}]$ is constant with respect to $\boldsymbol \theta$ and will disapear by differentiation, and
